Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-06-28 GWLDCII.tex
typo

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
  \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
  \end{itemize}
\end{lem}
Note that since the first condition tells us that $p$ has nothing inside it then then in the second condition if $q$ exists then $j<_ji<_jn-1$.

>>>>

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
  \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
  \end{itemize}
\end{lem}
Note that since the first condition tells us that $p$ has nothing inside it then in the second condition if $q$ exists then $j<_ji<_jn-1$.
